Tensor anisotropy as a tracer of cosmic voids

### 2015-03-10 cosmic_voids.tex
Acknowledgement to Nelson Padilla

We find that voids are distributed in two different  families
differentiated by the 
presence/absence of an overdense matter ridge in their density
profiles. 
To discriminate each void in one of the families we use the
compensation  index $\mathcal{C}$.
It is defined as the mass of a void enclosed in a spherical volume of
radius $R$ and normalized by the mass of the same volume assuming
it is filled by matter with the mean background density.

@@

As in the density these results also consistent with a Universial
velocity profile for voids \citep{Paz13, Hamaus14}.

@@

>>>>

We find that voids are distributed in two different families
differentiated by the 
presence/absence of an overdense matter ridge in their density
profiles. This result was also found by \citet{Ceccarelli13} when analysing
voids in the SDSS.
To discriminate each void in one of the families we use the
compensation  index $\mathcal{C}$.
It is defined as the mass of a void enclosed in a spherical volume of
radius $R$ and normalized by the mass of the same volume assuming
it is filled by matter with the mean background density.

@@

As in the density, these results are also consistent with a Universal
velocity profile for voids \citep{Paz13, Hamaus14}.

@@

We would like to thank Nelson Padilla for helpful comments and suggestions
on the manuscript.
